Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-10-05 paper/ifo-conclusions.tex
pass through text to edit language in a few places, shortened conclusion, added missing exhibition reference

In this paper, we use a table-top Michelson interferometer as an analogue to a gravitational-wave detector and demonstrate a range of signal processing techniques used within the GW community and more broadly. Gravitational-wave signals are simulated by playing sound recordings through a speaker which is fixed to the back of one of the arm mirrors. We consider quasi-monochromatic signals as an analogue to continuous wave signals as well as short segments of speech and music for more general interest. These recordings of complex audio could also serve as more distant analogues to un-modelled gravitational-wave bursts, e.g. from supernovae.

We demonstrate the recovery of a signal with constant frequency and signal with slowly wandering frequency in Sections~\ref{sec:ifo} and ~\ref{sec:single_tone}, respectively. We use a basic webcam with a sampling rate of $30\,{\rm Hz}$ to track the interference pattern. For the wandering frequency we successfully recover the injected signal using the Viterbi algorithm. These sections directly demonstrate the techniques used in continuous gravitational-wave searches.

In Section~\ref{sec:optical_microphone}, we demonstrate the recovery of more complex signals of music and speech. By substituting the webcam with a photodiode read by a Raspberry Pi, we transform the interferometer into an optical microphone by greatly increasing the sampling rate. We demonstrate that the optical microphone is capable of playing back simple recordings well but produces unintelligible recordings of speech. The mains signal at $50\,{\rm Hz}$ and its harmonics dominate the photodiode output. To recover the signal from under this noise we apply a hierarchy of filters and statistical techniques from signals processing, including a Butterworth band-pass filter and a notch filter, to a Wiener filter and the logMMSE estimator. We find that the logMMSE estimator works the best from those tried but still doesn’t enhance the speech to an intelligible level. This demonstration allows students to explore a variety of filtering and speech enhancement techniques. Further avenues of exploration include even more advanced processing techniques and a full characterisation of the transfer function of the system, with the goal to lead to improvements in intelligibility.

The demonstration presented here has great potential to be adapted for use in the undergraduate laboratory. It can be used to demonstrate topics such as interferometer physics; gravitational-wave detection, searches, and analysis; and signal processing with filters and speech enhancement techniques to physics and electrical engineering students. Given the increased level of excitement and public interest in the field of gravitational-wave astronomy in recent years, this table-top demonstration can be used as a tool for explaining gravitational-wave research to a wider, non-specialist audience. The future will bring many more detections, including further observations of transient signals from binary black hole and binary neutron star mergers, as well as the anticipated first detections of other classes of signal, including continuous waves, to which this demonstration provides some charming insights.

>>>>

In this paper, we use a table-top Michelson interferometer as an analogue to a gravitational-wave detector, demonstrating a range of signal processing techniques used within the gravitational-wave community and more broadly. Gravitational-wave signals are simulated by playing sound recordings through a speaker fixed to the back of one of the arm mirrors. We consider quasi-monochromatic signals as an analogue to continuous wave signals as well as short segments of speech and music for more general interest. These recordings of complex audio could also serve as more distant analogues to un-modelled gravitational-wave bursts, e.g. from supernovae.

% reduced detail for conclusion (trying to reduce overall length)
In Sections~\ref{sec:single_tone} and~\ref{sec:viterbi_wandering} we analyse audio signals with constant and wandering frequencies respectively as analogues to continuous gravitational wave signals. 
The wandering frequency signal is recovered using using the Viterbi algorithm. 
These sections directly demonstrate the techniques used in current continuous gravitational-wave searches. 
%We demonstrate the recovery of a signal with constant frequency and signal with slowly wandering frequency in Sections~\ref{sec:ifo} and ~\ref{sec:single_tone}, respectively. We use a basic webcam with a sampling rate of $30\,{\rm Hz}$ to track the interference pattern. For the wandering frequency we successfully recover the injected signal using the Viterbi algorithm. These sections directly demonstrate the techniques used in continuous gravitational-wave searches.

% again reducing overall length as we probably don't need to list everything
The recovery of more complex music and speech signals are demonstrated in Section~\ref{sec:optical_microphone}, where we treat the interferometer as an optical microphone. 
Simple music recordings can be recognised when played back, however speech remains unintelligible after applying a selection of filters and statistical techniques from signal processing. 
We find that the logMMSE estimator produces the best result of those applied here, however it does not enhance the recording to an intelligible level. 
This demonstration allows students to explore a variety of filtering and speech enhancement techniques. 
Further avenues of exploration to improve intelligibility are detailed in Section~\ref{sec:future_work}. 
%In Section~\ref{sec:optical_microphone}, we demonstrate the recovery of more complex signals of music and speech. By substituting the webcam with a photodiode read by a Raspberry Pi, we transform the interferometer into an optical microphone by greatly increasing the sampling rate. We demonstrate that the optical microphone is capable of playing back simple recordings well but produces unintelligible recordings of speech. The mains signal at $50\,{\rm Hz}$ and its harmonics dominate the photodiode output. To recover the signal from under this noise we apply a hierarchy of filters and statistical techniques from signals processing, including a Butterworth band-pass filter and a notch filter, to a Wiener filter and the logMMSE estimator. We find that the logMMSE estimator works the best from those tried but still doesn’t enhance the speech to an intelligible level. This demonstration allows students to explore a variety of filtering and speech enhancement techniques. Further avenues of exploration include even more advanced processing techniques and a full characterisation of the transfer function of the system, with the goal to lead to improvements in intelligibility.

The demonstration presented has potential to be adapted for use in the undergraduate laboratory.
It can be used to teach topics of interest to physics and electrical engineering students including, interferometer physics; gravitational-wave detection, searches, and analysis; and signal processing with filters and speech enhancement techniques. 
The increased excitement and public interest in the field of gravitational-wave research in recent years means that this demonstration may also be adapted as a tool for explaining gravitational-wave research to a wider, non-specialist audience. 
The field of gravitational-wave astrophysics continuous to grow and the future will bring many more detections of binary black holes and neutron stars, as well as the anticipated first detection of other classes of signals such as continuous waves to which this demonstration provides some charming insights. 
%The demonstration presented here has great potential to be adapted for use in the undergraduate laboratory. It can be used to demonstrate topics such as interferometer physics; gravitational-wave detection, searches, and analysis; and signal processing with filters and speech enhancement techniques to physics and electrical engineering students. Given the increased level of excitement and public interest in the field of gravitational-wave astronomy in recent years, this table-top demonstration can be used as a tool for explaining gravitational-wave research to a wider, non-specialist audience. The future will bring many more detections, including further observations of transient signals from binary black hole and binary neutron star mergers, as well as the anticipated first detections of other classes of signal, including continuous waves, to which this demonstration provides some charming insights.

### 2020-10-05 paper/ifo-futureWork.tex
pass through text to edit language in a few places, shortened conclusion, added missing exhibition reference

An initial improvement could be to better isolate the experiment, especially from the sources of mains noise. As the Raspberry Pi demands little power and connects to USB it could instead be powered with a commercial battery rather than the mains supply. All other components of the circuit, including the photodiode are connected to the Pi. The laser is DC powered through a converter, so should not couple noise from the mains into the interferometer. Transferring the circuit from a breadboard to a printed circuit board can also reduce interference~\cite{elfekey2013design}.
%With the interferometer in a dark room and under a box to better isolate from any ambient light or air currents, this would hopefully remove (or better separate) all sources of the 50Hz mains hum from the optical microphone.

We can consider improving the stability of the optical microphone components. A feedback loop control system can be used to suppress any unwanted movement of the interferometer components~\citep{abbott2017exploring, Sekiguchi:2016bmv, verhoeven2009robust}.

We can also benefit from fully characterizing the transfer function of the system as it provides the exact information of how audio signal couples through the interferometer. The total transfer function would start with the voltage being sent to the speaker and end with the voltage recorded by the Pi. It also would include any inherent non-linearities in the speaker, the speaker-mirror coupling, the path length to intensity relation (Appendix~\ref{app:intensity_derivation}), and the photodiode. The schematic in Fig.~\ref{fig:pipeline_highlighted} shows the signal flow through the system.
% commented out whilst James is checking this
% jam: I'm pretty confident this is what Rob said. 
%With perfect knowledge of the transfer function, signal recovery is limited by the signal-to-noise ratio as an optimal matched filter could be constructed.
%\jam{[check with Rob et al. about the veracity of this]}

A voluminous literature exists on using a hidden Markov model (HMM) trained on phonemes to recognize speech~\cite{HMM_english}. These could perform the final stage of speech enhancement for the optical microphone. Interestingly, this connects back to the Viterbi algorithm in Section~\ref{sec:viterbi_wandering}, which is also underpinned by a HMM, albeit of a different type. Alternatively, machine learning solutions exist throughout the field that are able to compete with statistical techniques such as the logMMSE estimator~\cite{SEGAN}.

We could also use more traditional techniques such as wavelet transform (WT) \citep{nason1995stationary} to extract the signal from noise, and compare these with the above methods. WT provides both time and frequency information, making it easier to pinpoint the origin of noise with respect to time. The authors in Refs.~\cite{tufekci2000feature,agbinya1996discrete} also proposed using WT for speech recognition.

Finally, considering the desire to demonstrate continuous GW analysis, further improvement of the optical microphone could lead to more advanced demonstration of techniques such as aiming or locking two or more optical microphones in an array.

@@

>>>>

% reduced length
Isolating the experiment from interference may provide some reduction in noise. 
For example, the Raspberry Pi could be powered with a commercial battery instead of mains power. 
%An initial improvement could be to better isolate the experiment, especially from the sources of mains noise. 
%As the Raspberry Pi demands little power and connects to USB it could instead be powered with a commercial battery rather than the mains supply. 
All other components of the circuit are connected to the Pi. 
%All other components of the circuit, including the photodiode are connected to the Pi. 
The laser is DC powered through a converter, so should not couple noise from the mains into the interferometer. 
Transferring the circuit from a breadboard to a printed circuit board can also reduce interference~\cite{elfekey2013design}.
%With the interferometer in a dark room and under a box to better isolate from any ambient light or air currents, this would hopefully remove (or better separate) all sources of the 50Hz mains hum from the optical microphone.
A feedback loop control system can also be used to suppress unwanted movement of the interferometer components~\citep{abbott2017exploring, Sekiguchi:2016bmv, verhoeven2009robust}, similar to methods used to isolate gravitational wave observatories. 
%We can consider improving the stability of the optical microphone components. A feedback loop control system can be used to suppress any unwanted movement of the interferometer components~\citep{abbott2017exploring, Sekiguchi:2016bmv, verhoeven2009robust}.

@@

A thorough characterisation of the systems transfer function would allow us to understand how audio signals couple through the interferometer. 
%We can also benefit from fully characterizing the transfer function of the system as it provides the exact information of how audio signal couples through the interferometer. 
The total transfer function starts with the voltage being sent to the speaker and ends with the voltage recorded by the Pi. It also would include any inherent non-linearities in the speaker, the speaker-mirror coupling, the path length to intensity relation (Appendix~\ref{app:intensity_derivation}), and the photodiode. The schematic in Fig.~\ref{fig:pipeline_highlighted} shows the signal flow through the system.
% commented out whilst James is checking this
% jam: I'm pretty confident this is what Rob said. 
%With perfect knowledge of the transfer function, signal recovery is limited by the signal-to-noise ratio as an optimal matched filter could be constructed.
%\jam{[check with Rob et al. about the veracity of this]}

A voluminous literature exists on using HMMs trained on phonemes to recognize speech~\cite{HMM_english}. These could perform the final stage of speech enhancement for the optical microphone. Interestingly, this connects back to the Viterbi algorithm in Section~\ref{sec:viterbi_wandering}, which is also underpinned by a HMM, albeit of a different type. Alternatively, machine learning solutions exist throughout the field that are able to compete with statistical techniques such as the logMMSE estimator~\cite{SEGAN}.

We could also use more traditional techniques such as wavelet transform (WT) \citep{nason1995stationary} to extract the signal from noise, and compare these with the above methods. WT provides both time and frequency information, making it easier to pinpoint the origin of noise with respect to time. In Refs.~\cite{tufekci2000feature,agbinya1996discrete} WT methods are proposed for speech recognition.

Returning to the demonstration of continuous gravitational wave analysis, further additions could include analysing data from multiple interferometers to extract directional information for audio signals. 
%Finally, considering the desire to demonstrate continuous wave analysis, further improvements to the optical microphone could lead to more advanced demonstration of techniques such as aiming or locking two or more optical microphones in an array.
% I think locking is the wrong word to use here as it is a word used a lot in GW instrumentation (an interferometer can be 'locked' on its own). I've tried to rephrase based on what I think you are getting at. -hannah

### 2020-10-05 paper/ifo-introduction.tex
Deeksha's comments: single and wandering tone
pass through text to edit language in a few places, shortened conclusion, added missing exhibition reference

In 2015, the first detection of gravitational waves from the merger of two black holes marked a breakthrough in modern astrophysics and revealed a new means to observe the universe~\cite{GW150914}.
% What are gws and gw detectors 
Gravitational waves, predicted by Albert Einstein in his theory of general relativity~\cite{Einstein:1916}, are disturbances in spacetime caused by the acceleration of asymmetric massive objects.
The effect of gravitational waves is a change in lengths: a `stretching and squeezing' of the distance between objects. 
Ground-based gravitational-wave observatories such as the Advanced Laser Interferometer Gravitational-wave Observatory (aLIGO~\cite{AdvancedLIGO:2015}), Advanced Virgo~\cite{AdvancedVirgo:2015}, GEO600~\cite{GEO600:2010}, and KAGRA~\cite{KAGRA:2013} use the interference of laser light to measure changes in distance. 
Gravitational-wave observatories are extremely complex but are fundamentally based on the Michelson interferometer. 
Table-top interferometers are commonly used in undergraduate laboratory experiments~\cite{UgoliniEtAl:2019} and to demonstrate the science of gravitational wave detection to non-specialist audiences~\cite{ThorLabsIFO,NikhefIFO,AMIGO:online,TTExhibit:2020,LIGOIFOGlue,LIGOIFOMagnets}.

% CW 
To date the network of gravitational-wave observatories has observed short-duration transient signals from the mergers of 
binary black holes~\cite{GW150914,GW151226,GW170104,GW170814,GW190521,GWTC-1:2018}, 
binary neutron stars~\cite{GW170817,GW170817multi,GW190425,GWTC-1:2018} and recently an observation of a black hole with an object that could either have been a neutron star or a black hole~\cite{GW190814}. 
However, the network is also searching for continuous gravitational waves: persistent, periodic, near-monochromatic signals, which are yet to be detected. 
Continuous waves may be emitted at a constant frequency or may wander slowly in frequency over time. 
Rotating neutron stars are prime candidates for continuous wave emission, especially those in low mass X-ray binaries (LMXB), where the neutron star is in orbit with a low mass stellar companion.
%where a compact object such as a black hole or a neutron star is in orbit with a low mass stellar companion.
% we're talking about neutron stars in LMXB's, so we don't need to mention black holes in LMXB's.
The rotation frequency of the neutron star can wander over time due to variable accretion of matter (and hence angular momentum transfer) from the stellar companion~\cite{xraybinaries:1997}. 
Scorpius X-1 is an LMXB which is particularly bright in X-rays, making it a prime target for continuous wave searches. %from LMXBs. 
Numerous, as yet unsuccessful, searches have been performed for Scorpius X-1 and other LMXBs~\cite{ScoX1O2Viterbi:2019, ScoX1ViterbiO1:2017, RadiometerO1O2:2019, SearchRadiometerO1:2017, SearchCrossCorrO1:2017, ScoX1ViterbiO1:2017, SearchTwoSpecS6:2017, MiddletonEtAlO2LMXBs:2020}.

In this paper, we present a table-top Michelson interferometer as a `toy' gravitational-wave detector designed to detect sound instead of gravitational waves. 
The demonstration can be used to teach topics ranging from continuous-wave detection and analysis to electronics, signal processing, and speech enhancement. 
%% I don't like the use of ``freedom to explore''.
Additionally, it allows students in courses such as physics and electrical engineering to explore the response of an accessible, yet nontrivial, opto-mechanical system using a hierarchy of data analysis techniques of increasing complexity, including those used in the search for continuous waves in LIGO and Virgo data~\cite{ScoX1O2Viterbi:2019, SuvorovaEtAl:2017,SuvorovaEtAl:2016}. 
% This demonstration can be adapted to an effective outreach tool to explain gravitational wave science to a non-specialist audience.
This demonstration also has the potential to be used as an outreach tool alongside other exhibitions~\cite{TTExhibit:2020,LIGOScienceEducationCentre:online,GravityDiscoveryCentre:online}, online data analysis tutorials~\cite{GWOSC:online,LOSC:2015}, phone applications~\cite{LaserLabs:online,SciVR:online,chirp:online}, online games~\cite{BlackHoleHunter:online}, and musical performances~\cite{ArthurJeffesMusic:online,GravitySynthLeonTrimble:online} which have been developed by gravitational wave research groups around the world. These tools allow scientists to cater to the increased public and media interest in this field and explain gravitational wave science to a non-specialist audience.
%\han{look up Sarah Farmer's project}

The design of the interferometer is detailed in Section~\ref{sec:ifo} and we demonstrate observing a single tone from a speaker in Section~\ref{sec:single_tone}. 
In Section~\ref{sec:viterbi_wandering} we replace the single tone with a wandering frequency signal and analyse the signal using a hidden Markov model technique (the Viterbi algorithm) from continuous wave searches. 
In Section~\ref{sec:optical_microphone}, we demonstrate capture and playback of complex audio, such as music and speech, to varying degrees of success.
This demonstration of an ‘optical microphone’ (using light to capture sound) serves as a more general exhibition of signal processing. 
We suggest avenues of future work in Section~\ref{sec:future_work} and draw conclusions in ~\ref{sec:conclusions}. 
Appendix~\ref{app:code} collects the software and scripts used to produce this work.

>>>>

In 2015, the first detection of gravitational waves from the merger of two black holes marked a breakthrough in modern astrophysics and revealed a new means to observe the universe~\cite{GW150914}.
% What are gws and gw detectors 
Gravitational waves are a prediction of Albert Einstein's theory of general relativity~\cite{Einstein:1916}, 
They are disturbances in spacetime caused by the acceleration of asymmetric massive objects.
The effect of gravitational waves is a change in lengths: a `stretching and squeezing' of the distance between objects. 
Ground-based gravitational-wave observatories such as the Advanced Laser Interferometer Gravitational-wave Observatory (LIGO~\cite{AdvancedLIGO:2015}), Advanced Virgo~\cite{AdvancedVirgo:2015}, GEO600~\cite{GEO600:2010}, and KAGRA~\cite{KAGRA:2013} use the interference of laser light to measure changes in distance. 
Gravitational-wave observatories are extremely complex but are fundamentally based on the Michelson interferometer. 
Table-top interferometers are commonly used in undergraduate laboratory experiments~\cite{UgoliniEtAl:2019} and to demonstrate the science of gravitational wave detection to non-specialist audiences~\cite{ThorLabsIFO,NikhefIFO,AMIGO:online,TTExhibit:2020,LIGOIFOGlue,LIGOIFOMagnets}.

% CW 
To date the network of gravitational-wave observatories has observed short-duration transient signals from the mergers of binary black holes~\cite{GW150914,GW151226,GW170104,GW170814,GW190521,GWTC-1:2018}, binary neutron stars~\cite{GW170817,GW170817multi,GW190425,GWTC-1:2018}, and recently the merger of black hole with an object that could either have been a neutron star or a black hole~\cite{GW190814}. 
However, the network is also searching for continuous gravitational waves: persistent, periodic, near-monochromatic signals, which are yet to be detected. 
Continuous waves may be emitted at a constant frequency or may wander slowly in frequency over time. 
Rotating neutron stars are prime candidates for continuous wave emission, especially those in low mass X-ray binaries (LMXB), where the neutron star is in orbit with a low mass stellar companion.
%where a compact object such as a black hole or a neutron star is in orbit with a low mass stellar companion.
% we're talking about neutron stars in LMXB's, so we don't need to mention black holes in LMXB's.
The rotation frequency of the neutron star can wander over time due to variable accretion of matter (and hence angular momentum transfer) from the stellar companion~\cite{xraybinaries:1997}. 
Scorpius X-1 is an LMXB which is particularly bright in X-rays, making it a prime target for continuous wave searches. %from LMXBs. 
Numerous, as yet unsuccessful, searches have been performed for Scorpius X-1 and other LMXBs~\cite{ScoX1O2Viterbi:2019, ScoX1ViterbiO1:2017, RadiometerO1O2:2019, SearchRadiometerO1:2017, SearchCrossCorrO1:2017, ScoX1ViterbiO1:2017, SearchTwoSpecS6:2017, MiddletonEtAlO2LMXBs:2020}.

% changed present to use, as this is not the first time a Michelson has been presented as a tpy GW detector - hannah
In this paper, we use a table-top Michelson interferometer as a `toy' gravitational-wave detector designed to detect sound instead of gravitational waves. 
% re-added "as an undergraduate experiment to be clear we are not talking about school teaching - hannah
As an undergraduate lab experiment, the demonstration can be used to teach topics ranging from continuous-wave detection and analysis to electronics, signal processing, and speech enhancement. 
%% I don't like the use of ``freedom to explore''. 
% removed Additionally - I don't think it is neccessary - hannah
It allows students in courses such as physics and electrical engineering to explore the response of an accessible, yet nontrivial, opto-mechanical system using a hierarchy of data analysis techniques of increasing complexity, including those used in the search for continuous waves in LIGO and Virgo data~\cite{ScoX1O2Viterbi:2019, SuvorovaEtAl:2017,SuvorovaEtAl:2016}. 
% This demonstration can be adapted to an effective outreach tool to explain gravitational wave science to a non-specialist audience.
% Rephrased as this kind of sounds like we are an exhibition too [hannah] - This demonstration also has the potential to be used as an outreach tool alongside other exhibitions
This demonstration also has the potential to be used as an outreach tool alongside a range of other public engagement demonstrations and activities including; hands-on demonstrations and exhibitions~\cite{TTExhibit:2020,CavagliaExhibit:2009,LIGOScienceEducationCentre:online,GravityDiscoveryCentre:online}, online data analysis tutorials~\cite{GWOSC:online,LOSC:2015}, phone applications~\cite{LaserLabs:online,SciVR:online,chirp:online}, online games~\cite{BlackHoleHunter:online}, and musical performances~\cite{ArthurJeffesMusic:online,GravitySynthLeonTrimble:online} which have been developed by gravitational-wave research groups around the world. 
These tools allow scientists to cater to the increased public and media interest in this field and explain gravitational-wave science to a non-specialist audience.
%\han{look up Sarah Farmer's project}

This paper is laid out as follows. 
In Section~\ref{sec:ifo} we detail the table-top interferometer design. 
We demonstrate observing a single tone from a speaker in Section~\ref{sec:single_tone}. 
In Section~\ref{sec:viterbi_wandering} we replace the single tone with a wandering frequency signal and analyse the signal using a hidden Markov model technique (the Viterbi algorithm) from continuous wave searches. 
In Section~\ref{sec:optical_microphone}, we demonstrate capture and playback of complex audio, such as music and speech.
% removed as there's not space to really say what this means here: to varying degrees of success.
This demonstration of an ‘optical microphone’ (using light to capture sound) serves as a more general exhibition of signal processing. 
We suggest avenues of future work in Section~\ref{sec:future_work} and draw conclusions in ~\ref{sec:conclusions}. 
Appendix~\ref{app:code} collects the software and scripts used to produce this work.

### 2020-10-05 paper/ifo-singleTone.tex
pass through text to edit language in a few places, shortened conclusion, added missing exhibition reference

Continuous-wave searches look for nearly monochromatic signals. In this section we consider a simple sinusoidal tone; a signal at a single constant frequency.

As described in Section~\ref{sec:ifo}, the audio signal is played through a speaker fixed to the back of M2. The intensity of the interference pattern is measured at a single point on the screen using a commercial USB webcam (see Fig.~\ref{fig:ifo_schematic_webcam}). The webcam samples at a rate of $30\,{\rm Hz}$, which limits the spectral content of observable signals to below $15\,{\rm Hz}$, the Nyquist frequency. A tone with a frequency of 2.09Hz is played through the speaker for one minute and the interference pattern is recorded by the webcam.

We take data from an off-centre pixel as indicated by the pink star in Fig.~\ref{fig:interference_pattern}. The pixel intensity in the green-channel of the video (the webcam records in three colour channels: red, blue, and green) is used to approximate the total intensity of the interference pattern. This is because the laser emits monochromatic green light at $532\,{\rm nm}$.
The amplitude of the Fourier transform of the recorded signal is shown in Fig.~\ref{fig:webcam_spectrum}. We measured a strong signal at $2.099\,{\rm Hz}$ with a full width half maximum (FWHM) of $0.033\,{\rm Hz}$. Although this range doesn't contain our injected frequency, the error is not substantial and cannot be heard by the (untrained) human ear.
Two harmonics can also be seen at integer multiples of the peak frequency. The peaks at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ have amplitudes of $0.103$ and $0.098$ as a fraction of the height of the main peak, respectively. They are likely due to the nonlinear response of the system discussed in Section~\ref{sec:ifo} and Appendix~\ref{app:intensity_derivation}.

>>>>

% rearranged as I found this section to switch between method and results too much, I've tried this order now: intro, webcam and data specifics, injection and results.

Continuous-wave searches look for nearly monochromatic signals. In this section we consider a simple sinusoidal tone; a single constant frequency.

As described in Section~\ref{sec:ifo}, the audio signal is played through a speaker fixed to the back of M2. 
The intensity of the interference pattern is measured at a single point on the screen, indicated by the pink star in Fig~\ref{fig:interference_pattern}. 
The webcam records video in three colour channels; red, blue, and green. 
We take the green channel as an approximation of the total intensity produced by the monochromatic green laser.
The webcam samples at a rate of $30\, {\rm Hz}$, which limits the spectral content of observable signals to less than $15\,{\rm Hz}$, the Nyquist frequency.

%The intensity of the interference pattern is measured at a single point on the screen using a commercial USB webcam (see Fig.~\ref{fig:ifo_schematic_webcam}). The webcam samples at a rate of $30\,{\rm Hz}$, which limits the spectral content of observable signals to below $15\,{\rm Hz}$, the Nyquist frequency. A tone with a frequency of $2.09\,{\rm Hz$} is played through the speaker for one minute and the interference pattern is recorded by the webcam.

%The pixel intensity in the green-channel of the video (the webcam records in three colour channels: red, blue, and green) is used to approximate the total intensity of the interference pattern. 
%This is because the laser emits monochromatic green light at $532\,{\rm nm}$.
A tone with a frequency of $2.09\,{\rm Hz}$ is played through the speaker for one minute. 
The amplitude of the Fourier transform of the recovered signal is shown in Fig.~\ref{fig:webcam_spectrum}. 
% removed 'strong' as what does strong mean here?
We measured a peak amplitude at $2.099\,{\rm Hz}$ with a full width half maximum (FWHM) of $0.033\,{\rm Hz}$. 
%Although this range doesn't contain our injected frequency, the error is not substantial and cannot be heard by the (untrained) human ear.
Two harmonics can also be seen at integer multiples of the peak frequency. 
The peaks at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ have amplitudes of $0.103$ and $0.098$ as a fraction of the height of the main peak, respectively. They are likely due to the nonlinear response of the system discussed in Section~\ref{sec:ifo} and Appendix~\ref{app:intensity_derivation}.
